---
title: "Lab4_StatisticalSloths"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`) #renaming `bwt/oz` because the "/" sign requires special care

```

# Does Smoking Lead to Babies Being Born Prematurely? 
* This question is interesting becuase it can help to better inform mothers about the risk that smoking can have on their unborn children, specifically if smoking can lead to a premature birth which can be extremely dangerous for children. This is important because knowing this may help to advise mothers to help avoid giving birth to children early, something that can affect the baby's well-being. 

```{r}
ggplot(data = babies) + 
  geom_bar(mapping = aes(x = Premature, fill =as.factor(number) ), position = "fill")
  
```


# Does Smoking Lead to Babies Being Born with Low Birth Weights?
* This question is interesting becuase it can help to better inform mothers about the risk that smoking can have on their unborn children, specifically if smoking can lead to low birth weights which can be very troubling for new born babies. This is important because knowing this may help to advise mothers to help avoid giving birth to children with dangerously low birth weights that could affect their health. 

```{r}
ggplot(data = babies) + 
  geom_smooth(mapping = aes(x=gestation, y=bwtoz, color=as.factor(smoke)), se=FALSE) + 
  xlab("Gestation Period Length") + 
  ylab("Birth Weight (oz)")
```
### Conclusion
* The data shows that generally, the babies of mothers who smoke have lower birth weights than of those who do not for almost all gestational ages. This means that the data does support the Surgeon General's second assertion.


* Why these questions are important, and why those reasons are important >

* Two plots (one per conclusion) that visually “answer” the two main questions

* Conclusions - is based on data, but could also be the logical consequence of a combination of findings. In this lab report, your conclusion should be the answer to your overall question. 

* Reccomendations - Inform your audience that there may be causally-relevant background characteristics not in the dataset that are not balanced in the two groups 

# Prelimary question

* Which variables are similar between smokers and nonsmokers? Which are different? 
    - Show the plots of the background variables which you believe have different distributions between smokers and     nonsmokers.
    

# Individual Sub Questions 


- Each individual should answer a unique question based on plots.
- We need 4 different geom functions!! 
- Show the plot or plots that lead you to the answer to your question. 
- Explicitly describe which non-default functions or aesthetics were used (e.g., aesthetic properties like shape, size, alpha, etc. and non-default facet functions, stat functions, coordinate functions, scale functions, theme functions, position adjustments, captions, labels, or legends).

Madeline's Plot 

Kevin's Plot
```{r}
ggplot(data = babies) + 
  geom_smooth(mapping = aes(x=parity, y=bwtoz), fill="green", size=2, level=0.85) + 
  xlab("# of All Previous Pregnancies") + 
  ylab("Birth Weight (oz)")
```
Kevin's Findings: 
* The babies of those who have had a higher number of previous pregnancies tend to have lower birth weights.

Katie's Plot 

Zandy's Plot:
ggplot(data = babies) +
  geom_jitter(mapping = aes( x =  , y = ),

* Summary of who did what and what non-defaults were used to generate which plots.
### Team Summary:
* I, Kevin Luth, created a plot answering the question of how the number of previous pregnancies had by someone affects their baby's birth weight. The data showed that child birth weights start to decrease as you get into higher numbers of previous pregnancies. I used the geom_smooth function and changed the color and width of the standard error interval to make it stand out on the gray background and to not have it overshadow the actual line. In addition, I changed the thickness of the line to make it more prominent on the page and in the error interval. I changed the x and y labels as well to more clearly display what they represent.






```{r}
cor(babies$smoke, babies$id)
cor(babies$smoke, babies$gestation)
cor(babies$smoke, babies$bwtoz)
cor(babies$smoke, babies$parity)
cor(babies$smoke, babies$mrace)
cor(babies$smoke, babies$mage)
cor(babies$smoke, babies$med)
cor(babies$smoke, babies$mht)
cor(babies$smoke, babies$mpregwt)
cor(babies$smoke, babies$drace)
cor(babies$smoke, babies$dage)
cor(babies$smoke, babies$ded)
cor(babies$smoke, babies$dht)
cor(babies$smoke, babies$dwt)
cor(babies$smoke, babies$marital)
cor(babies$smoke, babies$inc)
cor(babies$smoke, babies$smoke)
cor(babies$smoke, babies$time)
cor(babies$smoke, babies$number)
cor(babies$smoke, babies$Premature)

```







